Results

### 2025-12-01 article.qmd
docs: update figures and text

@fig-overview provides an overview of the selected time interval from Encounter 7, comparing measurements from the PSP (left panels) and Wind (right panels) missions. From top to bottom, the panels display 8-minute averages of the magnetic field magnitude, proton number density, and proton bulk flow speed, followed by ion and electron temperatures resolved in the parallel and perpendicular directions. To facilitate comparison, Wind data are scaled to $20 R_\odot$ using the empirical relations $B_{\text{scaled}}/B = ( 20 R_\odot / 1\ \text{AU} )^{-1.59}$, $n_{\text{scaled}}/n = ( 20 R_\odot / 1\ \text{AU} )^{-1.96}$ [@perroneRadialEvolutionSolar2019]. 
The fifth and sixth panels show the median Alfvén ratio, $R_{VB} = |Δ 𝐕| / |Δ 𝐕_A|$, of the current sheets and the total number of current sheets identified within each four-hour window. Including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$ does not significantly affect the Alfvén ratio $R_{VB}^* = R_{VB} / \sqrt{1 - Λ}$; its average value is approximately 0.5 for PSP and 0.4 for Wind over the entire time interval. The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
Panel (a.7) and (b.7) present the cross helicity and residual energy, which describe the Alfvénic nature and energetic balance of the ambient plasma, respectively, calculated every 8 minutes. The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind. These parameters offer critical insights into identifying the source regions of different solar wind streams [@altermanCrossHelicityHelium2025].

>>>>

@fig-overview provides an overview of the selected time interval from Encounter 7, comparing measurements from the PSP (left panels) and Wind (right panels) missions. From top to bottom, the panels display 8-minute averages of the magnetic field magnitude, proton number density, and proton bulk flow speed, followed by ion and electron temperatures resolved in the parallel and perpendicular directions. To facilitate comparison, Wind data are scaled to $20 R_\odot$ using the empirical relations $B_{\text{scaled}}/B = ( 20 R_\odot / 1\ \text{AU} )^{-1.59}$, $n_{\text{scaled}}/n = ( 20 R_\odot / 1\ \text{AU} )^{-1.96}$ [@perroneRadialEvolutionSolar2019]. 
The fifth and sixth panels show the median Alfvén ratio, $R_{VB} = |Δ 𝐕| / |Δ 𝐕_A|$, of the current sheets and the total number of current sheets identified within each four-hour window. Including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$ does not significantly affect the Alfvén ratio $R_{VB}^* = R_{VB} / \sqrt{1 - Λ}$; its average value is approximately 0.5 for PSP and 0.4 for Wind over the entire time interval. The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
Panels (a.7) and (b.7) present the cross helicity and residual energy, calculated every 8 minutes, which characterize the Alfvénic nature and energetic balance of the ambient plasma. We compute these quantities in the standard form: $\sigma_c = \frac{2 \langle \delta \mathbf{V} \cdot \delta \mathbf{V}_A \rangle}{ \langle\delta\mathbf{V}^2\rangle + \langle\delta\mathbf{V}_A^2\rangle }, \quad \sigma_r = \frac{\langle\delta \mathbf{V}^2\rangle-\langle\delta \mathbf{V}_A^2\rangle}{\langle\delta \mathbf{V}^2\rangle+\langle\delta \mathbf{V}_A^2\rangle},$ where $\delta \mathbf{V}$ and $\delta \mathbf{V}_A=\delta( \mathbf{B} / \sqrt{\mu_0 \rho})$ are the fluctuating velocity and Alfvén velocity, respectively. 
The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind. These parameters offer critical insights into identifying the source regions of different solar wind streams [@altermanCrossHelicityHelium2025].

### 2025-12-01 notebooks/01_demo.qmd
docs: update figures and text

TODO: Check Wind examples

```{julia}
using Random

f = Figure(size=(1800, 1000))

rows = rand(eachrow(df), min(5, nrow(df)))
for (plot_idx, i) in enumerate(rows)
    plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
end
f
```

@@

```{julia}
let df = dropmissing(psp_df, :duration)
    long_events = df[df.duration.> Second(30), :]
    println("Found $(nrow(long_events)) events with duration > 30 seconds")

@@

```{julia}
dt = Second(50)
map((psp_df, wind_df), timeranges) do _df, _tr
    df = dropmissing(_df, :duration)
    short_events = df[df.duration.< dt, :]
    n = nrow(short_events)
    occurence_rate = n / Float64(uconvert(u"d", _tr[2] - _tr[1]))
    println("Found $n events with duration < $dt")
    println("Occurence rate: $occurence_rate")
end

>>>>

## Check events with $B_n/B > 0.75$

```{julia}
f = Figure(size=(1800, 1000))
let df = filter_low_mva_quality(@subset(wind_df, :B_n_mva_norm .> 0.75)), 𝐁 = wind_conf["B"]
    rows = rand(eachrow(df), min(5, nrow(df)))
    for (plot_idx, row) in enumerate(rows)
        plot_candidate(f[1, plot_idx], row, 𝐁; add_B_mva=true)
    end
end

let df = filter_low_mva_quality(@subset(psp_df, :B_n_mva_norm .> 0.75)), 𝐁 = psp_conf["B"]
    rows = rand(eachrow(df), min(5, nrow(df)))
    for (plot_idx, row) in enumerate(rows)
        plot_candidate(f[2, plot_idx], row, 𝐁; add_B_mva=true)
    end
end
delete_legends!(f[1:2,1:4])
f
```

@@

```{julia}
(Ølet df = dropmissing(psp_df, :duration)
    long_events = df[df.duration.>Second(30), :]
    println("Found $(nrow(long_events)) events with duration > 30 seconds")

@@

```{julia}
dt = Second(50)
map((psp_df, wind_df), timeranges) do _df, _tr
    df = dropmissing(_df, :duration)
    short_events = df[df.duration.<dt, :]
    n = nrow(short_events)
    occurence_rate = n / Float64(uconvert(u"d", _tr[2] - _tr[1]))
    println("Found $n events with duration < $dt")
    println("Occurence rate: $occurence_rate")
end

### 2025-12-01 notebooks/02_stats.qmd
docs: update figures and text

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save, hide_facet_labels!, add_labels!
using AlgebraOfGraphics
using AlgebraOfGraphics: data
import AlgebraOfGraphics as AoG
using LinearAlgebra
using Accessors
using Unitful
Unitful.preferunits(u"nA", u"km")

@@

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
```

@@

_float64(x) = Float64(x)
_float64(::Missing) = missing

@@

@@

function plot_properties_hist(df, 𝐧)
    figure = (; size=(450, 600))
    𝒎 = var_mapping(; 𝐧)

    datalimits = x -> quantile(x, [0.01, 0.99])

    l_sym = first(𝒎.l_norm)
    tdf = @chain df begin
        @subset(.!isnan.($l_sym); view=true)
        subset_𝐧(𝐧)
        dropmissing(l_sym)
    end

    l_vars = [𝒎.l_log, 𝒎.l_norm_log]
    j_vars = [𝒎.j_log, 𝒎.j_norm_log]
    B_vars = [𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
    l_labels = ["Thickness", "Normalized thickness"]
    j_labels = ["Current density", "Normalized current density"]
    B_labels = ["|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]

    facet = (; linkxaxes=:none, linkyaxes=:none)
    layer = mapping(color=:id, linestyle=:enc) *
            AoG.density(; datalimits) * visual(Lines)
    axis = (; yscale=log10)

    plt = AoG.data(tdf) * mapping(l_vars, layout=AoG.dims(1)) * layer
    f = draw(plt; axis, figure, legend=(; position=:top))
    ylims!.(getproperty.(f.grid, :axis), 10^(-1.6), 10^(0.1))

    gl2 = GridLayout(f.figure[2, 1:end])
    f2 = draw!(gl2, AoG.data(tdf) * mapping(j_vars, layout=AoG.dims(1)) * layer; axis)

    gl3 = GridLayout(f.figure[3, 1:end])
    # no need to subset and dropmissing
    f3 = draw!(gl3, AoG.data(df) * mapping(B_vars, layout=AoG.dims(1)) * layer; axis)

    hide_facet_labels!.((f, f2, f3))
    rowgap!(f.figure.layout, 1)
    add_labels!(f.figure; position=Left(), padding=(20, -20, 0, 0))
    colgap!.((f.figure.layout, gl2, gl3), 1)

    return f
end

fs = map([:mva, :cross]) do 𝐧
    plot_properties_hist(df, 𝐧)
    # subset df by plasma beta
    # plot_properties_hist(@rsubset(df, :β < 1), 𝐧)
    # plot_properties_hist(@rsubset(df, :β > 3), 𝐧)
    # easy_save("$fname-$𝐧"; force=true)
    easy_save("$fname-$𝐧")
end
fs[1]
```

@@

    easy_save("duration_dist")
end
```

@@

    fig = Figure()
    ga = draw!(fig[1, 1], spec * mapping(ΔV_ratio))
    gb = draw!(fig[1, 2], spec * mapping(ΔV_cosθ))
    gc = draw!(fig[2, 1], spec * mapping(dB_over_B))
    gd = draw!(fig[2, 2], spec * mapping(dB_max_over_B))
    add_labels!(fig; valign=:top, position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    pretty_legend!(fig, ga)
    easy_save("Alfvenicities"; formats, force=true)
    # vars = [ΔV_cosθ, ΔV_ratio, dB_over_B, dB_max_over_B]
    # plt = spec * mapping(vars, layout=AoG.dims(1) => renamer(labels))
    # draw(plt, axis=(; yscale=log10), facet=(; linkyaxes=:minimal))
end
```

@@

```{julia}
function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha)) + AoG.data(psp_df)
end
```

```{julia}
layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"

for 𝐧 in [:mva, :cross]
    view = true
    𝒎 = var_mapping(; 𝐧)

@@

    add_labels!([fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]]; position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    # easy_save("joint_properties-$𝐧"; force=true)
    easy_save("joint_properties-$𝐧")
end
```

@@

```{julia}
layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"

for 𝐧 in [:mva, :cross], subset in (true)
    normalization = :column
    𝒎 = var_mapping(; 𝐧)
    B_sym = Symbol(:B_n_, 𝐧)
    tdf = dropmissing(df, B_sym)
    # tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
    tdf = subset_𝐧(tdf, 𝐧)
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
    f = draw(B_n_ω_spec)
    colgap!(f.figure.layout, 10)

    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
    ff = f.figure[0, 1:3]
    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
    rowgap!(f.figure.layout, 4)
    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
    # easy_save("B_n_ω_subset=$subset"; force=true)
    easy_save("B_n_ω_-$𝐧-subset=$subset")
end
```

```{julia}
layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"

for 𝐧 in [:mva], subset in (true, false)
    normalization = :column
    𝒎 = var_mapping(; 𝐧)
    tdf = dropmissing(df, :B_n_mva_norm)
    tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
    duration_spec = plt * mapping(:duration, 𝒎.ω_in)
    f = draw(duration_spec)
    display(f)
end
```

@@

let vars = [:Q_sonnerup, :duration, :σ_c]
    tdf = @chain df begin
        dropmissing(vars)
        @rsubset(all(!isnan, (:ΔV_cosθ, :Q_sonnerup, :σ_c)); view=true)
    end

    fig = Figure(; size=(500, 800))
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)

@@

    rowgap!(fig.layout, 4)
    for g in (grid3, grid4)
        ax = g[1].axis
        ax.xlabelpadding[] = 1
        ax.xlabelsize[] = 16
    end
    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 0, 0, -5))
    hide_facet_labels!.((grid2, grid3, grid4))
    easy_save("Q_sonnerup_joint_dist_den")
end
```

>>>>

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save, hide_facet_labels!, add_labels!
using Beforerr
using CategoricalArrays
using AlgebraOfGraphics
using AlgebraOfGraphics: data
import AlgebraOfGraphics as AoG
using LinearAlgebra
using Accessors
using Unitful
Unitful.preferunits(u"nA", u"km")

@@

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
# foreach([:log10, :log2, :log]) do f
# @eval import Base: $f
# @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
# end
set_Z_theme!()
```

@@

_float64(x) = passmissing(Float64)(x)

@@

thm_df = @rsubset(df, :id == "THEMIS"; view=true)
thm_df.id .= "ARTEMIS"
df.id = categorical(df.id)
levels!(df.id, ["PSP", "ARTEMIS", "Wind"])

@@

fs = map([:mva, :cross]) do 𝐧
    plot_properties_hist(df, 𝐧)
    # subset df by plasma beta
    # plot_properties_hist(@rsubset(df, :β < 1), 𝐧)
    # plot_properties_hist(@rsubset(df, :β > 3), 𝐧)
    easy_save("$fname-$𝐧"; force=true)
    # easy_save("$fname-$𝐧")
end
fs[1]
```

@@

    easy_save("duration_dist"; force=true)
end
```

@@

    fig = Figure()
    ga = draw!(fig[1, 1], spec * mapping(ΔV_ratio))
    gb = draw!(fig[1, 2], spec * mapping(ΔV_cosθ))
    gc = draw!(fig[2, 1], spec * mapping(dB_over_B))
    gd = draw!(fig[2, 2], spec * mapping(dB_max_over_B))
    add_labels!(fig; valign=:top, position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    pretty_legend!(fig, ga)
    easy_save("Alfvenicities"; force=true)
    # vars = [ΔV_cosθ, ΔV_ratio, dB_over_B, dB_max_over_B]
    # plt = spec * mapping(vars, layout=AoG.dims(1) => renamer(labels))
    # draw(plt, axis=(; yscale=log10), facet=(; linkyaxes=:minimal))
end
```

@@

```{julia}
function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id ∈ ("ARTEMIS", "THEMIS"); view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    AoG.data(psp_df) + (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha))
end
```

```{julia}
for 𝐧 in [:mva, :cross]
    view = true
    𝒎 = var_mapping(; 𝐧)

@@

    add_labels!([fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]]; position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    easy_save("joint_properties-$𝐧"; force=true)
    # easy_save("joint_properties-$𝐧")
end
```

@@

```{julia}
for 𝐧 in [:mva, :cross], subset in (true)
    normalization = :column
    𝒎 = var_mapping(; 𝐧)
    B_sym = Symbol(:B_n_, 𝐧)
    tdf = dropmissing(df, B_sym)
    # tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
    tdf = subset_𝐧(tdf, 𝐧)
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
    f = draw(B_n_ω_spec)
    colgap!(f.figure.layout, 10)

    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
    ff = f.figure[0, 1:3]
    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
    rowgap!(f.figure.layout, 4)
    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
    easy_save("B_n_ω_-$𝐧-subset=$subset"; force=true)
    # easy_save("B_n_ω_-$𝐧-subset=$subset")
end
```

![](../figures/B_n_ω_-mva-subset=true.png) and ![](../figures/B_n_ω_-mva-subset=false.png)

```{julia}
for 𝐧 in [:mva], subset in (true, false)
    normalization = :column
    𝒎 = var_mapping(; 𝐧)
    tdf = dropmissing(df, :B_n_mva_norm)
    tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
    duration_spec = plt * mapping(:duration, 𝒎.ω_in)
    f = draw(duration_spec)
    display(f)
end
```

@@

fig = Figure(; size=(500, 800))
let vars = [:Q_sonnerup, :duration, :σ_c]
    tdf = @chain df begin
        dropmissing(vars)
        @rsubset(all(!isnan, (:ΔV_cosθ, :Q_sonnerup, :σ_c)); view=true)
    end
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)

@@

    rowgap!(fig.layout, 4)
    for g in (grid3, grid4)
        ax = g[1].axis
        ax.xlabelpadding[] = 1
        ax.xlabelsize[] = 16
    end
    add_labels!([fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]]; position=Left(), padding=(0, 0, 0, -5))
    hide_facet_labels!.((grid2, grid3, grid4))
    easy_save("Q_sonnerup_joint_dist_den"; force=true)
end
```
